# Methods

`ggVennDiagram` is built on the shoulder of the other related R packages.
Except for `ggplot2`, it also depends on the functions in `dplyr`, `tibble`, `sf`, and so on.
Besides, the design of `ggVennDiagram` version 1.0 is inspired by two packages,
`venn` and `RVenn`.

## Predefined `sysdata` in `venn`

`venn::venn()` support Venn diagram up to 7 sets.

It use predefined values to plot polygons. 

```{r}
library(dplyr)
sets <- venn:::sets
glimpse(sets)
```

- s: number of sets;
- v: whether it is for ellipse;
- n: No. of polygons;

The following is a visualization of `venn` predefined polygons. 
These polygons can't be generated using simple functions, but are painstaking manual work 
that took years to create. I have communicated with the author of `venn`, Prof. Adrian Dușa, 
and get his consent to reuse these data.


```{r}
library(ggplot2)
ggplot(sets, aes(x,y)) + 
  geom_polygon(aes(color=factor(n)),alpha=1/5) + 
  facet_grid(v~s) + 
  coord_fixed() +
  theme_void() +
  theme(legend.position = "none")
```

In `ggVennDiagram`, we also store a predefined shapes in `sysdata`, and this 
will no doubt improve shape generations in user-side.
You may navigate the shape data with `get_shape_data()` function.

```{r}
ggVennDiagram::get_shape_data(4)
```

or plot them with `plot_shapes()`.

```{r}
ggVennDiagram::plot_shapes()
```


## Set operation in `RVenn`

`RVenn` defines a S4 class object `Venn` to store members of Venn sets.

```{r}
library(purrr)
library(RVenn)
library(ggplot2)
ggVennDiagram(gene_list)
```

Construct the Venn object.

```{r}
toy <- Venn(gene_list)
glimpse(toy)
```

On this basis, it implements methods to calculate the intersection/overlapping/union 
of different sets. 


### Set operations in `RVenn`

- **Intersection**

```{r}
# intersection
overlap(toy)
overlap(toy, slice = 1:3)
overlap(toy, slice = c("A","B","C"))
```

- **Union**

```{r}
unite(toy) %>% sort()
```

- **Set difference**

```{r}
discern(toy, slice1 = 1:3) %>% sort()
discern(toy, slice1 = 1:2, slice2 = 3:4) %>% sort()
```

In `ggVennDiagram`, region value calculation depends on the `RVenn` package and 
new functions written on its defined Venn object. 
There are totally $2^n–1$ regions in a Venn diagram, in which $n$ is the number of sets. 
We developed `discern_overlap()` to calculate the members of every Venn regions.
By default, it will return the intersection of all the sets, which only contains one gene here.


```{r}
discern_overlap(toy)
discern_overlap(toy, slice = 1:2)
```

We construct a `Polygon` object that inherits `Venn` to store shape data.
And expanded `discern_overlap()` method to calculate region shapes.
After calculation, the member and count of each region are stored with region ids in a tibble, 
and then joined with the region shape object by unique ids. Likewise, 
the member and count of sets are assigned to the `SetEdge` by unique ids in parallel.  
By doing this, a complete `VennPlotData` object is finished and can be used for plotting.


