--- 
title: "Venn Diagram cookbook in R"
author: "Chun-Hui Gao"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "How to draw Venn diagram with R packages."
---

```{r echo=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      fig.width = 7,
                      fig.asp = 0.618,
                      out.width = "90%")
Sys.setenv(LANGUAGE = "en") # 显示英文报错信息
```


# Preface

In this online book, I would like to compare the usage of several Venn Diagram 
tool in R environment. It is the investigation of these existing tools prompted 
me to develop a new tool `ggVennDiagram`.

## Prerequisites

List of packages

- `VennDiagram`
- `colorfulVennPlot`
- `venn`
- `nVennR`
- `eulerr`
- `venneuler`
- `gplots`
- `ggVennDiagram`
- `ggvenn`

You need to install these packages.

```{r}
cran_packages <- c("VennDiagram","colorfulVennPlot","gplots","venn",
                   "nVennR", "eulerr","venneuler","ggVennDiagram")
xfun::pkg_load2(cran_packages)

# GitHub
if (!requireNamespace("ggvenn")){
  remotes::install_github("yanlinlin82/ggvenn")
}
```



## Sessioninfo

```{r}
sessionInfo()
```

